Robustly decorrelating errors with mixed quantum gates

### 2019-08-02 decorrelation/mixed_unitaries.tex
more house cleaning

\subsubsection{Hamiltonian Norm Regularization}
\label{sec:norm}
The convex optimization problems discussed up until this point can be solved analytically, however casting them as convex optimization problems will allow us to add penalty terms to the cost function to promote different properties of the MQG. In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error. As an example, any MQG that mixes equally over equal and opposite errors will satisfy (\ref{eq:robust_minimization}), but depending on the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent error.\note{Just give an explicit example.} To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians. In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm:

>>>>

\subsubsection{Hamiltonian Norm Regularization}
\label{sec:norm}
The convex optimization problems discussed up until this point can be solved analytically, however casting them as convex optimization problems will allow us to add penalty terms to the cost function to promote different properties of the MQG. In particular, while (\ref{eq:robust_minimization}) is sufficient for suppressing the diamond norm to first order relative to the \textit{worst} controls in the collection, it does not preferentially select the controls with the least error. As an example, any MQG that mixes equally over equal and opposite errors will satisfy (\ref{eq:robust_minimization}), but the magnitude of the error of the resulting channel will depend on the magnitude of the original coherent errors. To encourage the inclusion of controls with smaller error, we may impose a penalty proportional to the norm of the included Hamiltonians. In our case, we choose to penalize for the $\ell_2$ ($||\cdot||_2$) norm:
